Nuclear Wastes bla bla bla

### 2017-01-14 paper.tex
outline joel comments

\section{Formation of (High-Level) Nuclear Waste}
    \subsection{Classification of Nuclear Waste}
    The IAEA classifies nuclear waste by considering the activity content and the half-life
    of the radionuclides (see FIG. \ref{fig:scheme}). Activity content is a measure of how much nuclear activity
    a given amount of wastes contain: a form of waste may possesses a high activity content due to
    a high concentration or high activity.\cite{iaea09}
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.7\textwidth]{wastescheme.png}
        \caption{An illustration of the IAEA classification scheme for nuclear wastes.\cite{iaea09}}
        \label{fig:scheme}
    \end{figure}

>>>>

\section{Nuclear Waste}
    \subsection{Classification of Nuclear Waste}
    Different organizations have slightly different classification schemes for nuclear waste.
    The International Atomic Energy Agency (IAEA) classifies nuclear waste by considering the activity content and the half-life
    of the radionuclides (see FIG. \ref{fig:scheme}). Activity content is a measure of how much nuclear activity
    a given amount of wastes contain: a form of waste may possesses a high activity content due to
    a high concentration or high activity.\cite{iaea09}
    \begin{figure}[h]
        \centering
        \includegraphics[width=0.7\textwidth]{wastescheme.png}
        \caption{An illustration of the IAEA classification scheme for nuclear wastes.\cite{iaea09}}
        \label{fig:scheme}
    \end{figure}
